Using Genetic Algorithms to Optimize the Analog Method for Precipitation Downscaling in the Swiss Alps

### 2016-11-07 AtmoSwing - GMD/template.tex
Updating affiliations.

\affil[1]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
\affil[2]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
\affil[3]{Terranum SARL, Bussigny, Switzerland}
\affil[4]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

>>>>

\affil[1]{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}
\affil[2]{University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
\affil[3]{Terranum SARL, Bussigny, Switzerland}
\affil[4]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

### 2016-11-07 Genetic algorithms - MWR/template.tex
Updating affiliations.

\affiliation{University of Lausanne, Lausanne, Switzerland and Oeschger Centre for Climate Change Research and Institute of Geography, University of Bern, Bern, Switzerland}

@@

\extraauthor{Michel Jaboyedoff}
\extraaffil{University of Lausanne, Lausanne, Switzerland}

>>>>

\affiliation{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland and University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}

@@

\extraauthor{Michel Jaboyedoff}
\extraaffil{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}

### 2016-11-07 Moving temporal window - HESS/template.tex
Updating affiliations.

\affil[1]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
\affil[2]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

@@

The Analog Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects \citep{Lorenz1956, Lorenz1969}. Multiple variations of the methods exist and listings can be found in \citet{Horton2016} or \citet{BenDaoud2015}. The versions that will be considered here are often used as references or benchmarks for various improvements.

@@

Then, $N_{1}$ dates with the lowest values of $S_{\text{TW}}$ are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate. Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day. Following the nomenclature proposed by \citet{Horton2016}, this method will be named 2Z.

>>>>

\affil[1]{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}
\affil[2]{University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
\affil[3]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

@@

The Analog Method (AM) is based on the principle that two relatively similar synoptic situations may produce relatively similar local effects \citep{Lorenz1956, Lorenz1969}. Multiple variations of the methods exist and listings can be found in \citet{BenDaoud2016}. The versions that will be considered here are often used as references or benchmarks for various improvements.

@@

Then, $N_{1}$ dates with the lowest values of $S_{\text{TW}}$ are considered as analogs to the target day, $N_{1}$ being a parameter to calibrate. Then, the daily observed precipitation amount of the corresponding dates provide the empirical conditional distribution considered as the probabilistic prediction for the target day. This method will be named 2Z further on.

### 2016-11-07 Optimization case study - JoH/elsarticle-template.tex
Updating affiliations.

\address[unil]{Institute of Earth Sciences, University of Lausanne, Lausanne, Switzerland}
\address[unibe]{Oeschger Centre for Climate Change Research \& Institute of Geography, University of Bern, Bern, Switzerland}
\address[terranum]{Terranum SARL, Bussigny, Switzerland}
\address[lthe]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}

>>>>

\address[unil]{University of Lausanne, Institute of Earth Sciences, Lausanne, Switzerland}
\address[unibe]{University of Bern, Oeschger Centre for Climate Change Research, Institute of Geography, Bern, Switzerland}
\address[terranum]{Terranum SARL, Bussigny, Switzerland}
\address[lthe]{Universit\'{e} de Grenoble-Alpes, LTHE, Grenoble, France}
